Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-02 scagnostics.Rmd
Collecting data for updated Table 1, still needs formatting.

```{r indexTable, echo=FALSE}
i <- 1
pLabels <- c("Spiral 100", "Spiral 1000", "Pipe 100", "Pipe 1000", "Sine 100", "Sine 1000")
indexOverview <- tibble(convex=numeric(),
               skinny=numeric(),
               stringy=numeric(),
               dcor2d=numeric(),
               splines2d=numeric(),
               MIC=numeric(),
               TIC=numeric(),
               holes=numeric(),
               name=character(),
               vars=character())
dsL <- list(spiral100, spiral1000, pipe100, pipe1000, sin100, sin1000)
for(ds in dsL){
  for(vars in list(c("V1","V2"),c("V5","V6"),c("V1","V6"))){
    dprj <- as.matrix(select_(ds, vars[1], vars[2]))
    scagRes <- scagnostics(dprj)
    dcorRes <- dcor2d(dprj[,1], dprj[,2])
    splineRes <- splines2d(dprj[,1], dprj[,2])
    mineRes <- mine(dprj[,1], dprj[,2])
    holesRes <- holes(dprj)
    indexOverview <- add_row(indexOverview, convex=scagRes[,"Convex"],
                    skinny=scagRes[,"Skinny"], stringy=scagRes[,"Stringy"],
                    dcor2d=dcorRes, splines2d=splineRes,
                    MIC=mineRes$MIC, TIC=mineRes$TIC, holes=holesRes,
                    name=pLabels[i], vars=paste0(vars[1],"-",vars[2]))
  }
  i <- i+1
}
knitr::kable(indexOverview,  caption = "Summary of index values.", digits=2) 
```

>>>>

FIXME yes/no labels appear to be inverted?

```{r indexTable, echo=FALSE}
tableTemp <- function(){
  tibble(
    index=character(),
    data=character(),
    size=numeric(),
    structured=character(),
    value5=numeric(),
    value95=numeric()
  )
}

getSample <- function(dataT, size){
  if (dataT == "Pipe"){
    ret <- pipeData(p = size, n = 6) %>% scale() %>% as_tibble()
  }
  if (dataT == "Spiral"){
    ret <- spiralData(p = size, n = 6) %>% scale() %>% as_tibble()
  }
  if (dataT == "Sine"){
    ret <- sinData(p = size, n = 6) %>% scale() %>% as_tibble()
  }
  return(ret)
}

getIdx <- function(dataT, size, structured){
  convex <- numeric(length = 100)
  skinny <- numeric(length = 100)
  stringy <- numeric(length = 100)
  micidx <- numeric(length = 100)
  ticidx <- numeric(length = 100)
  dcor2D <- numeric(length = 100)
  splines2D <- numeric(length = 100)
  for(i in 1:100){
    cSample <- getSample(dataT, size)
    if(structured){
      x = as.numeric(cSample$V1)
      y = as.numeric(cSample$V2)
    } else{
      x = as.numeric(cSample$V5)
      y = as.numeric(cSample$V6)
    }
    scag <- scagnostics(x=x, y=y)$s
    midx <- mine(x, y, est = "mic_e")
    skinny[i] <- scag["Skinny"]
    stringy[i] <- scag["Stringy"]
    convex[i] <- scag["Convex"]
    micidx[i] <- midx$MIC
    ticidx[i] <- midx$TIC
    dcor2D[i] <- dcor2d(x=x, y=y)
    splines2D[i] <- splines2d(x,y)
  }
  lapply(c(skinny, stringy, convex, micidx, ticidx, dcor2D, splines2D), sort)
  res <- tableTemp() %>%
    add_row(index="Skinny", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=skinny[5], value95=skinny[95]) %>%
    add_row(index="Stringy", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=stringy[5], value95=stringy[95]) %>%
    add_row(index="Convex", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=convex[5], value95=convex[95]) %>%
    add_row(index="MICe", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=micidx[5], value95=micidx[95]) %>%
    add_row(index="TICe", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=ticidx[5], value95=ticidx[95]) %>%
    add_row(index="dcor2D", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=dcor2D[5], value95=dcor2D[95]) %>%
    add_row(index="splines2D", data=dataT, size=size,
            structured=ifelse(structured, "yes", "no"),
            value5=splines2D[5], value95=splines2D[95])
}

if(!file.exists("cache/indexTable.rda")){
  set.seed(505)
  res <- tableTemp()
  for(ds in c("Pipe", "Sine", "Spiral")){
    for (size in c(100, 1000)){
      for (structured in c(TRUE, FALSE)){
        res <- full_join(res,getIdx(ds, size, structured))
      }
    }
  }
  save(res, file = "cache/indexTable.rda")
} else {
  load("cache/indexTable.rda")
}
knitr::kable(res,  caption = "Summary of index values.", digits=2) 
```
